Filling in the Gaps: Using Consumer Products to Replace Missing Pollution Data

### 2022-03-07 paper/15min-presentation/15min-presentation.tex
Adding _short OLS table for presentation

%---------------------------------------------------------
%Purple Air Outdoor Monitors
\begin{frame}
\frametitle{Purple Air Outdoor Monitors}
\hspace{1em}
Purple Air Sensors in California 
\hspace{4em}
LA Site Example \\

@@

%---------------------------------------------------------
%Alternate measure of ambient air quality
\begin{frame}
\frametitle{Alternate measure of ambient air quality}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Predicting Missing EPA Data
\begin{frame}
\frametitle{Predicting Missing EPA Data}
\end{frame}
%---------------------------------------------------------

@@

>>>>

%---------------------------------------------------------
%Purple Air Outdoor Monitors
\begin{frame}
\frametitle{PurpleAir Outdoor Monitors}
\hspace{1em}
PurpleAir Sensors in California 
\hspace{4em}
LA Site Example \\

@@

%---------------------------------------------------------
%Alternate measure of ambient air quality
\begin{frame}
\frametitle{Alternate measure of ambient PM2.5 Concentration}

\hspace{7em}
\includegraphics[width=0.5\textwidth]{output/figures/diagrams/IDW_diagram.png}
\\
\textbf{Inverse-distance Weighted Average Ambient PM2.5}

\begin{equation*}
    PA^{IDW}_t= \sum\limits_{j=1}^{J_t} \dfrac{\frac{1}{d_j}\cdot PA_{j,t}}{\sum\limits_j^{J_t}\frac{1}{d_j}}
    = \sum\limits_{j=1}^{J^t} w_{j,t}\cdot PA_{j,t}
\end{equation*}
\begin{itemize}
    \item $J_t$ = active PurpleAir sensors around the NAAQS monitor at time $t$
\end{itemize}

%---------------------------------------------------------
%Predicting Missing EPA Data
\begin{frame}
\frametitle{Predicting Missing EPA Data}
\begin{equation*}
EPA_t = \beta_0 + \beta_1 PA^{IDW}_t + \varepsilon_t
\end{equation*}

\input{pics/appendix/tables/epa_OLS_idw_pa_site-037-4004_short}
\end{frame}
%---------------------------------------------------------

@@

%---------------------------------------------------------
% Purple Air EPA Correction
\begin{frame}
\frametitle{Correction of PurpleAir Readings}
$$
\widetilde{PA}_{j,t}=\begin{cases}
			0.52*PA_{j,t} - 0.086*H_{j,t} + 5.75, & \text{if $PA_{j,t} \leq 343 \mu$g/m$^3$}\\
            0.46*PA_{j,t} + 0.(3.93e-4)PA_{j,t}^2 + 2.97, & \text{otherwise}
		 \end{cases}
$$
\begin{itemize}
    \item $PA_{j,t}$ = ambient PM2.5 measured by PurpleAir sensor $j$ at time $t$
    \item $H_{j,t}\in[0,1]$ is the relative humidity
\end{itemize}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
% Future Prediction Equation
\begin{frame}
\frametitle{Better Prediction of EPA PM2.5}

$$
\widetilde{PA}_{j,t}=\begin{cases}
			0.52*PA_{j,t} - 0.086*H_{j,t} + 5.75, & \text{if $PA_{j,t} \leq 343 \mu$g/m$^3$}\\
            0.46*PA_{j,t} + 0.(3.93e-4)PA_{j,t}^2 + 2.97, & \text{otherwise}
		 \end{cases}
$$
\begin{itemize}
    \item $PA_{j,t}$ = ambient PM2.5 measured by PurpleAir sensor $j$ at time $t$
    \item $H_{j,t}\in[0,1]$ is the relative humidity
\end{itemize}
\end{frame}
%---------------------------------------------------------
